How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

Figure~\ref{fig5} shows the permeability and anisotropy measurements for the complete data set. In particular, for a given number of initial bodies ($M$ = 20, 40, 60, 80, or 100), the mean and standard deviation of each quantity are shown, and the five different values of $M$ are shown by different colors. As seen in Figures~\ref{fig5}(a)--(b), the trends of increasing permeabilities are well grouped by the number of initial bodies. That is, permeability monotonically decreases with the number of bodies and the error bars shows little overlap between different values of $M$ until very late in the simulation when the bodies have nearly vanished.

@@

Similar statistical analysis is performed on the tortuosity measurements and shown in Figure~\ref{fig6}(a)--(b). Much like before, the tortuosity measurements are well separated by the number of bodies, with the error bars showing little overlap across different values of $M$. Measurements of the tortuosity ratio, $(T_2 -1)/(T_1 -1)$, however, show similar behavior across different values of $M$, as seen in Figure~\ref{fig6}(c). For nearly all runs, the tortuosity ratio increases as bodies erode up to a maximum of roughly $(T_2 -1)/(T_1 -1) = 8$, and then the tortuosity ratio decreases near the very end of the simulation. As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figures~\ref{fig6}(d)--(e). The shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.

>>>>

Figure~\ref{fig5} shows the permeability and anisotropy measurements for the complete data set. In particular, for a given number of initial bodies ($M$ = 20, 40, 60, 80, or 100), the mean and standard deviation of each quantity are shown, with different values of $M$ shown by different colors. As seen in Figures~\ref{fig5}(a)--(b), the trends of increasing permeabilities are well grouped by the number of initial bodies. That is, permeability monotonically decreases with the number of bodies and the error bars shows little overlap between different values of $M$ until very late in the simulation when the bodies have nearly vanished.

@@

Similar statistical analysis is performed on the tortuosity measurements and shown in Figure~\ref{fig6}(a)--(b). In all simulations, the longitudinal tortuosity decreases with time as erosion allows passive tracers to take more direct paths when traveling in the flow direction. In contrast, Fig.~\ref{fig6}(b) shows the transverse tortuosity can increase with time, as passive tracers must work to circumvent horizontally aligned bodies when traveling in the vertical direction.
Measurements of the tortuosity ratio, $(T_2 -1)/(T_1 -1)$ show similar behavior across different values of $M$, as seen in Figure~\ref{fig6}(c). For nearly all runs, the tortuosity ratio increases as bodies erode, and maximum ratio of roughly $(T_2 -1)/(T_1 -1) = 8$ is reached. Finally, the tortuosity ratio decreases near the very end of the simulation. As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figures~\ref{fig6}(d)--(e). The shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.
